\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-12-22 overview.tex
update

The goal of our work is to detect distributed system bugs \emph{before} they reach production. Distributed systems typically consist of multiple components that interact with each other via \emph{message passing}. If these messages---or unexpected failures and timeouts---are not handled properly, they can lead to subtle bugs. To expose these bugs, we use \psharp~\cite{deligiannis2015psharp}, an extension of the \csharp language that provides: (i) language support for \emph{modeling} the environment of distributed systems written in .NET; and (ii) a \emph{systematic testing engine} that can explore interleavings between \emph{distributed events}, such as the nondeterministic order of message deliveries, failures and timeouts. If the \psharp testing engine identifies a sequence of events that triggers a bug (witnessed by an assertion failure), then exploration terminates, and a trace is reported.

>>>>

The goal of our work is to detect distributed system bugs \emph{before} they reach production. Distributed systems typically consist of multiple components that interact with each other via \emph{message passing}. If these messages---or unexpected failures and timeouts---are not handled properly, they can lead to subtle bugs. To expose these bugs, we use \psharp~\cite{deligiannis2015psharp}, an extension of the \csharp language that provides: (i) language support for \emph{modeling} the environment of distributed systems written in .NET; and (ii) a \emph{systematic testing engine} that can explore interleavings between \emph{distributed events}, such as the nondeterministic order of message deliveries, failures and timeouts.

Modeling using \psharp involves two core activities. First, the developer must modify the original system so that messages are not sent through the real network, but are instead dispatched using the \psharp \texttt{Send} method. Such modification is typically non-invasive, as it can be performed with dynamic dispatch, a \csharp language feature already used for unit testing. Second, the developer must write a \psharp test harness that nondeterministically triggers various distributed events, such as client requests, failures and timeouts. The purpose of these two modeling activities is to explicitly declare all possible sources of nondeterminism in the distributed system using \psharp.

During testing, the \psharp runtime is aware of all sources of nondeterminism that were declared during the modeling process, and exploits this knowledge to create a scheduling point each time a nondeterministic choice has to be evaluated. The \psharp systematic testing engine will serialize the system (in single-box setup), and repeatedly execute it from start to completion, each time exploring a potentially different set of nondeterministic choices, until it either reaches a bound (e.g. in number of executions or time), or it hits a safety or liveness property violation (see \S\ref{sec:overview:bugs}). This testing process is fully automatic, has no false-positives (assuming an accurate test harness), and can reproduce found bugs by replaying buggy schedules. After a bug is found, the \psharp testing engine generates a trace that represents the buggy schedule. In contrast to logs typically generated during production, the \psharp trace provides a global order of all communication events, and thus is easier to debug.
